---
title: "R Notebook"
output: html_notebook
---

```{r}
require(flexmix)
require(TraMineR)
require(TraMineRextras)
require(dplyr)
require(stringr)
library(tidyr)


NSLY97Data <- read.csv("ProcessedDF.csv", header=TRUE, stringsAsFactors=FALSE)
NSLY97Data$ID <- seq(1, 3551)

NSLY97Data <- NSLY97Data %>%
  select(-X)

#Sample <- read.csv("ProperSample.csv", header=TRUE, stringsAsFactors=FALSE)





```


```{r}
#Get Values 
age_columns <- grep("_\\d+$", names(NSLY97Data), value = TRUE)

non_age_columns <- setdiff(names(NSLY97Data), age_columns)

# Reshape the data
LongNSLY97Data <- NSLY97Data %>%
  pivot_longer(
    cols = all_of(age_columns),
    names_to = c(".value", "t"),
    names_pattern = "(.*)_(\\d+)$"
  ) %>%
  mutate(t = as.integer(t))  # Ensure 't' is an integer

# Reorder columns if needed
LongNSLY97Data <- LongNSLY97Data %>%
  select(all_of(non_age_columns), t, everything())

LongNSLY97Data$EducationStat <- as.factor(LongNSLY97Data$EducationStat)
LongNSLY97Data$EmploymentStatus <- as.factor(LongNSLY97Data$EMP_HOURS)

LongNSLY97Data$t <- LongNSLY97Data$t - 16

#LongNSLY97Data$t <- as.factor(LongNSLY97Data$t)

LongNSLY97Data <- LongNSLY97Data %>%
  select(-EMP_HOURS)

LongNSLY97Data$HasSibling <- as.factor(LongNSLY97Data$HasSibling)
LongNSLY97Data$Sex <- as.factor(LongNSLY97Data$Sex)
LongNSLY97Data$SingleorDoubleParent <- as.factor(LongNSLY97Data$SingleorDoubleParent)
#LongNSLY97Data$FinalRelationshipStat <- as.factor(LongNSLY97Data$FinalRelationshipStat)
```




```{r}
LongNSLY97DataLag <- LongNSLY97Data %>%
  group_by(ID) %>%
  mutate(FinalRelationshipStatLag1 = lag(FinalRelationshipStat, n = 1)) %>%
  ungroup()
```

```{r}
# Generates code to create the Data for Logistic Regression and Random Forest Trees
write.csv(LongNSLY97Data, "NSLYData.csv")
write.csv(LongNSLY97DataLag, "WithLaggedData.csv")
```


## Generating the Production Model with ALL the Data used for Training

```{r}
Krange <- 11:11  #SLOW!!!
nRep <- 1 #number of random starts (slow, but important)


set.seed(23675)
##if (!exists("fmm3")) { # check whether data is loaded

Comp11FullDS <- stepFlexmix(.~0|ID, k=Krange, nrep=nRep,
                    model=FLXMRmultinom(FinalRelationshipStat~t+Sex+SingleorDoubleParent+EmploymentStatus+EducationStat+HasSibling),
                    data=LongNSLY97Data, control=list(verbose=1, minprior=0.025))
```



```{r}


SamplesToRemove <- read.csv("ProperSample.csv", header=TRUE, stringsAsFactors=FALSE)
TheSampleList<-SamplesToRemove['X0']

LongNSLY97Data <- LongNSLY97Data %>% 
  filter(!ID %in% TheSampleList$X0)


```

## Code for Generating the Model with an 80:20 Train/Test Split


```{r}
Krange <- 3:14  #SLOW!!!
nRep <- 1 #number of random starts (slow, but important)


set.seed(23675)
##if (!exists("fmm3")) { # check whether data is loaded

FullRangeForBIC <- stepFlexmix(.~0|ID, k=Krange, nrep=nRep,
                    model=FLXMRmultinom(FinalRelationshipStat~t+Sex+SingleorDoubleParent+EmploymentStatus+EducationStat+HasSibling),
                    data=LongNSLY97Data, control=list(verbose=1, minprior=0.025))
```



```{r}
LongNSLY97DataLag <- LongNSLY97Data %>%
  group_by(ID) %>%
  mutate(FinalRelationshipStatLag1 = lag(FinalRelationshipStat, n = 1)) %>%
  ungroup()

LongNSLY97DataLag$FinalRelationshipStatLag1[is.na(LongNSLY97DataLag$FinalRelationshipStatLag1)] <- 99

LongNSLY97DataLag$FinalRelationshipStat <- as.factor(LongNSLY97DataLag$FinalRelationshipStat)
LongNSLY97DataLag$FinalRelationshipStatLag1 <- as.factor(LongNSLY97DataLag$FinalRelationshipStatLag1)

LongNSLY97Data$FinalRelationshipStat <- as.factor(LongNSLY97Data$FinalRelationshipStat)


```


```{r}
Krange <- 3:3  #SLOW!!!
nRep <- 2 #number of random starts (slow, but important)


set.seed(87654)
##if (!exists("fmm3")) { # check whether data is loaded

NineTryConverge <- stepFlexmix(.~0|ID, k=Krange, nrep=nRep,
                    model=FLXMRmultinom(FinalRelationshipStat~t+Sex+SingleorDoubleParent+EmploymentStatus+EducationStat+HasSibling+FinalRelationshipStatLag1),
                    data=LongNSLY97DataLag, control=list(verbose=1, minprior=0.05,iter.max=1000,tolerance = 5e-08))
```



## How we got the value for the FirstDataset



### USE MODEL THAT WAS TRAINED ON THE TRAIN DATASET SO THAT WE CAN CLASSIFY IT OTHER MODELS # LOAD FullRangeForBIC


```{r}
filename <- file.choose()
FinalResultSetTrain <- readRDS(filename)
```

```{r}
BIC(FinalResultSetTrain)
AIC(FinalResultSetTrain)
```


```{r}
PosteriorCheck <- FinalResultSetTrain@models[[9]]@posterior$scaled
```

```{r}
head(PosteriorCheck)
```



```{r}
usemodel <- FinalResultSetTrain@models[[9]]

comp <- lapply(usemodel@components, "[[", 1)

Matrix1 <- comp$Comp.1@parameters$coef
Matrix2 <- comp$Comp.2@parameters$coef
Matrix3 <- comp$Comp.3@parameters$coef
Matrix4 <- comp$Comp.4@parameters$coef
Matrix5 <- comp$Comp.5@parameters$coef
Matrix6 <- comp$Comp.6@parameters$coef
Matrix7 <- comp$Comp.7@parameters$coef
Matrix8 <- comp$Comp.8@parameters$coef
Matrix9 <- comp$Comp.9@parameters$coef
Matrix10 <- comp$Comp.10@parameters$coef
Matrix11 <- comp$Comp.11@parameters$coef



XMatrix <- usemodel@model[[1]]@x
YMatrix <- usemodel@model[[1]]@y


Priors <- usemodel@prior

write.csv(as.data.frame(Matrix1), 'coef1.csv', row.names = FALSE)
write.csv(as.data.frame(Matrix2), 'coef2.csv', row.names = FALSE)
write.csv(as.data.frame(Matrix3), 'coef3.csv', row.names = FALSE)
write.csv(as.data.frame(Matrix4), 'coef4.csv', row.names = FALSE)
write.csv(as.data.frame(Matrix5), 'coef5.csv', row.names = FALSE)
write.csv(as.data.frame(Matrix6), 'coef6.csv', row.names = FALSE)
write.csv(as.data.frame(Matrix7), 'coef7.csv', row.names = FALSE)
write.csv(as.data.frame(Matrix8), 'coef8.csv', row.names = FALSE)
write.csv(as.data.frame(Matrix9), 'coef9.csv', row.names = FALSE)
write.csv(as.data.frame(Matrix10), 'coef10.csv', row.names = FALSE)
write.csv(as.data.frame(Matrix11), 'coef11.csv', row.names = FALSE)


write.csv(as.data.frame(Priors), 'Priors.csv', row.names = FALSE)



```


# This is the value of the FULL Coefficient SET. All RECORDS ARE INCLUDED # LOAD Comp11FullDS

```{r}
filename <- file.choose()
FinalResultSet <- readRDS(filename)
```


```{r}
BIC(FinalResultSet)
```



```{r}
usemodel <- FinalResultSet

comp <- lapply(usemodel@components, "[[", 1)

Matrix1 <- comp$Comp.1@parameters$coef
Matrix2 <- comp$Comp.2@parameters$coef
Matrix3 <- comp$Comp.3@parameters$coef
Matrix4 <- comp$Comp.4@parameters$coef
Matrix5 <- comp$Comp.5@parameters$coef
Matrix6 <- comp$Comp.6@parameters$coef
Matrix7 <- comp$Comp.7@parameters$coef
Matrix8 <- comp$Comp.8@parameters$coef
Matrix9 <- comp$Comp.9@parameters$coef
Matrix10 <- comp$Comp.10@parameters$coef
Matrix11 <- comp$Comp.11@parameters$coef



XMatrix <- usemodel@model[[1]]@x
YMatrix <- usemodel@model[[1]]@y


Priors <- usemodel@prior

write.csv(as.data.frame(Matrix1), 'coef1full.csv', row.names = FALSE)
write.csv(as.data.frame(Matrix2), 'coef2full.csv', row.names = FALSE)
write.csv(as.data.frame(Matrix3), 'coef3full.csv', row.names = FALSE)
write.csv(as.data.frame(Matrix4), 'coef4full.csv', row.names = FALSE)
write.csv(as.data.frame(Matrix5), 'coef5full.csv', row.names = FALSE)
write.csv(as.data.frame(Matrix6), 'coef6full.csv', row.names = FALSE)
write.csv(as.data.frame(Matrix7), 'coef7full.csv', row.names = FALSE)
write.csv(as.data.frame(Matrix8), 'coef8full.csv', row.names = FALSE)
write.csv(as.data.frame(Matrix9), 'coef9full.csv', row.names = FALSE)
write.csv(as.data.frame(Matrix10), 'coef10full.csv', row.names = FALSE)
write.csv(as.data.frame(Matrix11), 'coef11full.csv', row.names = FALSE)

write.csv(as.data.frame(XMatrix), 'XMatrixfull.csv', row.names = FALSE)
write.csv(as.data.frame(YMatrix), 'YMatrixfull.csv', row.names = FALSE)
write.csv(as.data.frame(Priors), 'PriorsFull.csv', row.names = FALSE)
write.csv(as.data.frame(ClusterClassification), 'ClusterClassification.csv', row.names = FALSE)

```


# DUMMY CODE TO EXTRACT FORMATTED DS COMPONENTS # LOAD THE DUMMYFILE

```{r}
filename <- file.choose()
DummyModel <- readRDS(filename)
```


```{r}
XMatrix <- DummyModel@model[[1]]@x
YMatrix <- DummyModel@model[[1]]@y


write.csv(as.data.frame(XMatrix), 'ARXMatrix.csv', row.names = FALSE)
write.csv(as.data.frame(YMatrix), 'ARYMatrix.csv', row.names = FALSE)

```



#CODE TO GET THE COMPONENTS OF THE DATASET WITH AR LAG 1 # LOAD OneLastModel


```{r}
filename <- file.choose()
FinalResultSetTrainAR1 <- readRDS(filename)

```

```{r}
BIC(FinalResultSetTrainAR1)
```
```{r}
AIC(FinalResultSetTrainAR1)
```




```{r}
usemodel <- FinalResultSetTrainAR1@models[[3]]

comp <- lapply(usemodel@components, "[[", 1)

Matrix1 <- comp$Comp.1@parameters$coef
Matrix2 <- comp$Comp.2@parameters$coef
Matrix3 <- comp$Comp.3@parameters$coef
Matrix4 <- comp$Comp.4@parameters$coef
#Matrix5 <- comp$Comp.5@parameters$coef
#Matrix6 <- comp$Comp.6@parameters$coef
#Matrix7 <- comp$Comp.7@parameters$coef
#Matrix8 <- comp$Comp.8@parameters$coef
#Matrix9 <- comp$Comp.9@parameters$coef
#Matrix10 <- comp$Comp.10@parameters$coef
#Matrix11 <- comp$Comp.11@parameters$coef



XMatrix <- usemodel@model[[1]]@x
YMatrix <- usemodel@model[[1]]@y


Priors <- usemodel@prior


```

```{r}

write.csv(as.data.frame(Matrix1), 'ARcoef1full.csv', row.names = FALSE)
write.csv(as.data.frame(Matrix2), 'ARcoef2full.csv', row.names = FALSE)
write.csv(as.data.frame(Matrix3), 'ARcoef3full.csv', row.names = FALSE)
write.csv(as.data.frame(Matrix4), 'ARcoef4full.csv', row.names = FALSE)
#write.csv(as.data.frame(Matrix5), 'ARcoef5full.csv', row.names = FALSE)
#write.csv(as.data.frame(Matrix6), 'ARcoef6full.csv', row.names = FALSE)
#write.csv(as.data.frame(Matrix7), 'ARcoef7full.csv', row.names = FALSE)
#write.csv(as.data.frame(Matrix8), 'ARcoef8full.csv', row.names = FALSE)
#write.csv(as.data.frame(Matrix9), 'ARcoef9full.csv', row.names = FALSE)
#write.csv(as.data.frame(Matrix10), 'ARcoef10full.csv', row.names = FALSE)
#write.csv(as.data.frame(Matrix11), 'ARcoef11full.csv', row.names = FALSE)

#write.csv(as.data.frame(XMatrix), 'ARXMatrix.csv', row.names = FALSE)
#write.csv(as.data.frame(YMatrix), 'ARYMatrix.csv', row.names = FALSE)
write.csv(as.data.frame(Priors), 'ARPriorsFull.csv', row.names = FALSE)

#probClass.1 <- usemodel@posterior$scaled

#ClusterClassificationAR <- apply(probClass.1,1,which.max)

#write.csv(as.data.frame(ClusterClassificationAR), 'ClusterClassificationAR.csv', row.names = FALSE)
```



```{r}
filename <- file.choose()
FinalResultSetTrainAR1 <- readRDS(filename)

```




```{r}
BIC(FinalResultSetTrainAR1)
```



